A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
small edits

Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying. We ask workers what languages they speak and what country they reside in, and validate their claims by measuring their ability to correctly translate words, and by geolocating them.  To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.  These tasks each consist of translating 12 foreign words into English.  Two of the 12 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 new entries.

@@

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/turkermap}
\caption{}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
&\# languages&\# Turkers\\ \hline
No languages&0&1801\\
One language&1&3154\\
Multiple languages&2&243	\\
&3&49\\
&4&12\\
&5&9\\
&6&5\\
&7&2\\
&8&1\\
&9&2\\
&10&2\\
&15&1\\
\hline\\hline
\end{tabular}
\label{numlangs-tab}
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying. We ask workers what languages they speak and in what country they reside, and validate their claims by measuring their ability to correctly translate words and by geolocating them.  To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.  These tasks each consist of translating 10 foreign words into English.  Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 new entries.

\textbf{***Is this right? I think most of our tasks have 10 words per HIT.***}

@@

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/turkermap-color}
\caption{}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accept tasks.

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
&\# languages&\# Turkers\\ \hline
No languages&0&1801\\
One language&1&3154\\
Multiple languages&2&243	\\
&3&49\\
&4&12\\
&5&9\\
&6&5\\
&7&2\\
&8&1\\
&9&2\\
&10&2\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
